---
title             : "Authoritarian Values and Colorblindness"
shorttitle        : "AVCB"

author: 
  - name          : "Kaila Scott-Charles"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
    role: # Contributorship roles (e.g., CRediT, https://credit.niso.org/)
      - "Conceptualization"
      - "Writing - Original Draft Preparation" 
      - "Writing - Review & Editing"
  - name          : "Isobel Heck"
    affiliation   : "2"
    role:
      - "Writing - Review & Editing"
      - "Supervision"

affiliation:
  - id            : "1"
    institution   : "University of Chicago"
  - id            : "2"
    institution   : "University of Rochester"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  One or two sentences to put the results into a more **general context**.
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : "r-references.bib"

floatsintext      : no
linenumbers       : yes
draft             : no
mask              : no

figurelist        : no
tablelist         : no
footnotelist      : no

classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)

```

# this is a graph
```{r}
#source("Assignment 2.R")

```
# **Heading 1 (bolded)**  
xyz

## *Heading 2 (italicized)*  
xyz

### Heading 3  
xyz  

# Starting Lists from HW5

**Unordered list**

* This is the first line in my unordered list
* Here is another line in the list
    + This is an indented line
* Here is another line in the unordered list


**Ordered List**  

1. First line
2. Second line
3. Third line
    + Item 3a
    + Item 3b



**Here, I am inserting a url**  
[This is a link to the RStudio website](https://www.rstudio.com)

<!-- This is my HTML-style comment. I can see this, but it won't show up when I knit the document -->


```{r call-function, echo=TRUE}
#Assignment 5 - call function
source("functions.R")


```


# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.


# Results

# Discussion


\newpage

# References

::: {#refs custom-style="Bibliography"}
:::
