---
title             : "Authoritarian Values and Colorblindness"
shorttitle        : "AVCB"

author: 
  - name          : "Kaila Scott-Charles"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
    role: # Contributorship roles (e.g., CRediT, https://credit.niso.org/)
      - "Conceptualization"
      - "Writing - Original Draft Preparation" 
      - "Writing - Review & Editing"
  - name          : "Isobel Heck"
    affiliation   : "2"
    role:
      - "Writing - Review & Editing"
      - "Supervision"

affiliation:
  - id            : "1"
    institution   : "University of Chicago"
  - id            : "2"
    institution   : "University of Rochester"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  One or two sentences to put the results into a more **general context**.
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : "r-references.bib"

floatsintext      : no
linenumbers       : yes
draft             : no
mask              : no

figurelist        : no
tablelist         : no
footnotelist      : no

classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)

```

```{r}
#load packages

library(dplyr)
library(tidyverse)
library(readr)

```

```{r load data, include=FALSE}
AVCB_wp_kids <- read.csv("AVCB_wp_kids.csv", na.strings = c("", "NA", "#N/A"))
AVCB_wp_parents <- read.csv("AVCB_wp_parents.csv", na.strings = "")

```

```{r combine files, include=FALSE}
#combine files
AVCB_wp_dyads <- merge(AVCB_wp_kids, AVCB_wp_parents, by = "Family_ID")

#renaming variables
AVCB_wp_dyads <- rename(AVCB_wp_dyads, "Single Child ID" = "ID.x")
AVCB_wp_dyads <- rename(AVCB_wp_dyads, "All Child IDs" = "ID.y")
AVCB_wp_dyads <- rename(AVCB_wp_dyads, "Child Version" = "Version.x")
AVCB_wp_dyads <- rename(AVCB_wp_dyads, "Parent Version" = "Version.y")
AVCB_wp_dyads <- rename(AVCB_wp_dyads, "Child_CB_Self_choice" = "CB_Self_choice.x")
AVCB_wp_dyads <- rename(AVCB_wp_dyads, "Parent_CB_Self_choice" = "CB_Self_choice.y")

```

```{r create intermediate dataset, include=FALSE}
#Checking column names before creating ID
print(names(AVCB_wp_dyads))

AVCB_wp_dyads_ID <- AVCB_wp_dyads |> 
  select(Family_ID:Gender, P1_Race.Eth, P2_Race.Eth, P1_pol:P2_ed, Child_CB_Self_choice, CB_Parents_choice, RE_Ind_Self_choice:Parent_sum, RE_Ind:WB_Cons,COBRAS_1_num:AV_sum)

#moving AV choice variables tgo right before AV num variables (for parents) - will want to rename these later so that it's clear which ones are kid vs. parent variables

AVCB_wp_dyads_ID <- AVCB_wp_dyads_ID |> 
  relocate(RE_Ind:WB_Cons, .before = RE_Ind_num)

AVCB_wp_dyads_ID

#Checking column names
print(names(AVCB_wp_dyads_ID))

```

```{r save intermediate dataset, include=FALSE}
write_csv(AVCB_wp_dyads_ID, "AVCB_wp_dyads_ID.csv")

```

# **Heading 1 (bolded)**  
xyz

## *Heading 2 (italicized)*  
xyz

### Heading 3  
xyz  

# Starting Lists from HW5

**Unordered list**

* This is the first line in my unordered list
* Here is another line in the list
    + This is an indented line
* Here is another line in the unordered list


**Ordered List**  

1. First line
2. Second line
3. Third line
    + Item 3a
    + Item 3b



**Here, I am inserting a url**  
[This is a link to the RStudio website](https://www.rstudio.com)

<!-- This is my HTML-style comment. I can see this, but it won't show up when I knit the document -->


```{r call-function, echo=FALSE}
#Assignment 5 - call function
#source("functions.R")
#hello_world("Kaila")

```
# **Mock up 2 plots (of 2 different types) you could include in your final report**

# **H1 Plot**
```{r H1 Plot, eval=TRUE, include=TRUE}
#H1: Parents’ authoritarian values will positively predict children’s own authoritarian values and this relation will strengthen with age.    
    
    #My idea for a graph: Scatterplot with parent AV score on x axis, child AV score on y axis with child age in different colors (6-10 years) 
    
    #Natalie's Suggestion: Scatterplot with parent AV score on x axis, child AV score on y axis  + smooth line with age plotted in different colors 

AVCB_H1 <-read.csv("AVCB_H1.csv")

library(ggplot2)

ggplot(
  data = AVCB_H1,
  mapping = aes(x = as.numeric(AV_sum), y = Self_sum, color = Years)
) +
  geom_point() +
  geom_smooth(method = "lm")

#I think I will need to transform the AV variables to percentage of times AV vs. non-AV trait was picked out of 4 trials??
#I'm noticing there's not a lot of variation within each measurement which makes graph look weird?
```

# **H2 Plot**
This hypothesis has 2 ways to test the question. This is because we tested kids' diversity ideology one way (binary choice), but we tested parents' diversity ideology two ways: 1) same binary choice measure, 2) A continuous scale measure. I will create a plot for both ways.
```{r H2 Plot, eval=TRUE, message = FALSE, warning=FALSE}
#H2: Parents’ diversity ideology will positively predict children’s own diversity ideology, and this relation will strengthen with age.   
    
###For child binary/parent continuous: 

#My way: Grouped Barplot with child classroom choice (binary) on x axis and parent COBRA score on y axis, plot age with different colored bars

AVCB_H2 <- read.csv("AVCB_H2.csv")

ggplot(AVCB_H2, aes(x = Child_Class_Self_choice, y = COBRAS_avg, fill = Child_Class_Self_choice)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Grouped Bar Plot",
       x = "Child Classroom Choice",
       y = "Parent COBRA Score") +
  scale_fill_manual(values = c("CC" = "blue", "CB" = "red")) + # Customize fill colors if needed 
  facet_grid(~Years)

#I need to take out NAs
#Is this best way to do this?

#Natalie's Suggestion: 2 Boxplots of parent COBRA score comparing kids who choose CC vs. kids who choose CB 
#My Q: But how do I add kids' age into this plot????

ggplot(AVCB_H2, aes(x = Child_Class_Self_choice, y = COBRAS_avg)) +
  geom_boxplot() + labs(title = "Side-by-Side Box Plots")

#I need to take out NAs
#I need to figure out how to look at this by age too since my hypothesis is that this relation will strengthen with age

##For child binary/parent binary: 

#My way: Stacked barchart with child classroom choice (binary) on x axis with each bar broken down by parent classroom choice (binary)

ggplot(AVCB_H2, aes(x = Child_Class_Self_choice, fill = Parent_Class_Self_choice)) +
  geom_bar(position = "dodge") +
  labs(title = "Grouped Bar Plot",
       x = "Variable1",
       y = "Count") +
  scale_fill_manual(values = c("CB" = "blue", "CC" = "red"))  # Customize fill colors if needed

#Natalie Suggestion: ??? Forgot to ask during final project meeting
```


```{r H3 Plot, eval=TRUE, message = FALSE, warning= FALSE}
#Will work on this one later
#H3: Higher authoritarian values will positively predict more colorblind attitudes.
    #For parents: Scatterplot with parent AV score on x axis, parent COBRA score on y axis
    #For kids: Barplot with child classroom choice (binary) on x axis and child AV score on y axis
    #Natalie's Suggestion: 2 Boxplots of parent AV score comparing kids who choose CC vs. kids who choose CB
      #But how do I add kids' age into this plot????

```



# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.


# Results

# Discussion


\newpage

# References

::: {#refs custom-style="Bibliography"}
:::
